### 2015-05-13 Draft/related.tex
Added Reference to another related work

Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664} from source code and binaries. 
Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  
\textit{micropatterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
In contrast, \tool\ infers specifications from the natural language text in API documents,
thus complementing existing approaches when the source code or binaries of the API library is not available.

>>>>

Another set of approaches infer code-contract-like specifications (such as behavioral model, algebraic specifications, and exception specifications) either dynamically\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105} or statically~\cite{Flanagan2001:HAA,Buse:2008:ADI:1390630.1390664,wasylkowski2011mining} from source code and binaries. 
Among mining based approaches Gable and Su~\cite{gabel2008javert} proposed to learn  
\textit{micropatterns} of temporal properties from runtime traces and then combining them into larger specifications depicted as finite state automata.
In contrast, \tool\ infers specifications from the natural language text in API documents,
thus complementing existing approaches when the source code or binaries of the API library is not available.
